---
title: "Math 240 Final Project"
author: "Zev Rosen"
date: "11/6/2019"
output: html_document
---

```{r}
library(tidyverse)
library(HH)
library(leaps)
library(car)
happiness <- read_csv("Happiness.csv")
names(happiness)
summaryHH(happiness)
names(happiness)
names(happiness)[1] <- "Country"
names(happiness)[4] <- "SDLadder"
names(happiness)[5] <- "Positive"
names(happiness)[6] <- "Negative"
names(happiness)[7] <- "Socialsupport"
names(happiness)[11] <- "Loggdppercapita"
names(happiness)[12] <- "Healthylifeexpectancy"
```

```{r}
fit <- lm(Score ~ Positive + Negative + Socialsupport + Freedom + Corruption + Generosity + Loggdppercapita + Healthylifeexpectancy, data = happiness)
fitsel = regsubsets(Score ~ Positive + Negative + Socialsupport + Freedom + Corruption + Generosity + Loggdppercapita + Healthylifeexpectancy, data = happiness, nbest = 2)
cbind(summary(fitsel)$which, summary(fitsel)$adjr2)
plot(fitsel, scale = "adjr2")
plot(fitsel, scale = "Cp")
plot(fitsel, scale = "bic")
summaryHH(fitsel)
fitsel2 = lm(Score ~ Positive + Negative + Socialsupport + Freedom + Corruption + Loggdppercapita + Healthylifeexpectancy, data = happiness)
vif(fitsel2)
fitsel3 <- lm(Score ~ Positive + Negative + Socialsupport + Freedom + Corruption + Loggdppercapita +
    Healthylifeexpectancy, data = happiness)
pairs(~Score + Positive + Negative + Socialsupport + Freedom + Corruption + Loggdppercapita +
    Healthylifeexpectancy, data = happiness)
plot(fitsel3$fitted.values, fitsel3$residuals, ylab = "residuals",
  xlab = "fitted y", main = "Residuals ")








fitsel3 <- lm(Score ~ Positive + Negative + Socialsupport + Freedom + Corruption  +
    Healthylifeexpectancy, data = happiness)
di = rstandard(fitsel3) # standardized residuals
ri = rstudent(fitsel3) # studentized residuals```
plot(fitsel3$fitted.values, ri, main="Studentized residuals versus fitted values")
abline(0,0)
qqnorm(ri)
qqline(ri)
selri = which(abs(ri) >= 3)
selri
happiness[c(133,148),]
fitsel3[selri]
outlierTest(fitsel3)
```
```{r}
fitsel3 <- lm(Score ~ Positive + Negative + Socialsupport + Freedom + Corruption  +
    Healthylifeexpectancy, data = happiness)
boxplot(happiness$Score, main = "Boxplot of Happiness Score", cex.main = 0.8, ylab = "happiness score")
hist(happiness$Score, xlab = "happiness", main = "Histogram of happiness score", cex.main = 0.8)
summary(happiness$Score)
IQR(happiness$Score, na.rm = T)
sd(happiness$Score, na.rm = T)

boxplot(happiness$Positive, main = "Boxplot of Positive Affect", cex.main = 0.8, ylab = "Positive Affect")
hist(happiness$Positive, xlab = "positive affect", main = "Histogram of Positive Affect", cex.main = 0.8)
IQR(happiness$Positive, na.rm = T)
sd(happiness$Positive, na.rm = T)
summary(happiness$Positive)

boxplot(happiness$Negative, main = "Boxplot of Negative Affect", cex.main = 0.8, ylab = "Negative Affect")
hist(happiness$Negative, xlab = "negative affect", main = "Histogram of Negative Affect", cex.main = 0.8)
IQR(happiness$Negative, na.rm = T)
sd(happiness$Negative, na.rm = T)
summary(happiness$Negative)

boxplot(happiness$Socialsupport, main = "Boxplot of Social Support", cex.main = 0.8, ylab = "social support")
hist(happiness$Socialsupport, xlab = "social support", main = "Histogram of social support", cex.main = 0.8)
IQR(happiness$Socialsupport, na.rm = T)
sd(happiness$Socialsupport, na.rm = T)
summary(happiness$Socialsupport)

boxplot(happiness$Freedom, main = "Boxplot of Freedom", cex.main = 0.8, ylab = "freedom")
hist(happiness$Freedom, xlab = "freedom", main = "Histogram of freedom", cex.main = 0.8)
IQR(happiness$Freedom, na.rm = T)
sd(happiness$Freedom, na.rm = T)
summary(happiness$Freedom)

boxplot(happiness$Corruption, main = "Boxplot of Corruption", cex.main = 0.8, ylab = "corruption")
hist(happiness$Corruption, xlab = "corruption", main = "Histogram of corruption", cex.main = 0.8)
IQR(happiness$Corruption, na.rm = T)
sd(happiness$Corruption, na.rm = T)
summary(happiness$Corruption)

boxplot(happiness$Healthylifeexpectancy, main = "Boxplot of Healthy Life Expectancy", cex.main = 0.8, ylab = "corruption")
hist(happiness$Healthylifeexpectancy, xlab = "healthy life expectancy", main = "Histogram of healthy life expectancy", cex.main = 0.8)
IQR(happiness$Healthylifeexpectancy, na.rm = T)
sd(happiness$Healthylifeexpectancy, na.rm = T)
summary(happiness$Healthylifeexpectancy)




```

